The Astropy Project:

### 2017-09-29 main.tex
velocities

    \item[Derivatives of coordinate representations]
    As mentioned above, the \texttt{Representation} classes act like
    three-dimensional vectors.
    \texttt{astropy.coordinates} now also supports handling first derivatives of
    the \texttt{Representation} classes through the new \texttt{Differential}
    classes.
    The \texttt{Differential} classes are currently used internal to the
    \texttt{Frame} classes to store velocity data when attached to a
    \texttt{Representation} instance.

    TODO: differential classes. Represent single-derivatives of
    representations. Used to store velocity information, only really useful
    attached to a representation object.

    \item[Proper motion and velocity transformations]
    TODO: Frame classes support proper motions, radial velocities. Explain
    component naming, why SkyCoord doesn't support right now, "experimental" but
    tested feature.

    \item[JPL ephemeris]
    TODO: JPL ephemerids % Who can write this? Erik?
\end{description}

>>>>

    \item[Proper motion and velocity transformations]
    In addition to positional coordinate data, the \texttt{Frame} classes now
    also support velocity data.
    As the default representation for most frames is spherical, most of the
    \texttt{Frame} classes expect proper motion and radial velocity components
    to specify the velocity information.
    The names of the proper motion components all start with \texttt{pm_} and
    adopt the same longitude and latitude names as the positional components.
    Transforming coordinates with velocity data is also supported, but in some
    cases the transformed velocity components have limited accuracy because the
    transformations are done numerically.
    The visualization of the coordinate frame transform graph highlights which
    velocity transformations can be done exactly and which transformations are
    done using a finite-difference scheme.
    The low-level interface for specifying and transforming velocity data (see
    the next point) is currently experimental.
    As such, in v2.0, only the \texttt{Frame} classes (and not the
    \texttt{SkyCoord} class) support handling velocities.

    \item[Derivatives of coordinate representations]
    As mentioned above, the \texttt{Representation} classes act like
    three-dimensional vectors.
    \texttt{astropy.coordinates} now also supports handling first derivatives of
    vectors / representations through the new \texttt{Differential} classes.
    The \texttt{Differential} classes are currently used internally within the
    \texttt{Frame} classes to store the velocity data.

    \item[JPL ephemeris]
    TODO: JPL ephemerids % Erik?
\end{description}
